### 2023-08-31 manuscript.tex
Added discussion about differences between gene and species trees

\subsection{Inference of species trees}
Many phylogenetic methods require a species tree to inform the evolutionary relationships between sequences. In fact, the phylo-HMMs discussed previously used a species tree as an input, though we omitted this detail for clarity of exposition. Therefore, to support the curation step and other downstream analyses, we sought to infer phylogenetic trees from the aligned sequences. However, since the roots of phylogenetic trees are not identifiable with commonly used time-reversible substitution models, we repeated the orthology inference pipeline with the outgroup species \textit{Scaptodrosophila lebanonensis}. Afterwards, we inferred phylogenetic trees using the LG model of amino acid substitution from 100 meta-alignments sampled from alignments of single copy orthologous groups. We then combined them into a single consensus tree (Fig.~\ref{fig:trees}A). To provide a similar tree for the analysis of non-coding regions, we inferred phylogenetic trees using the GTR model of nucleotide substitution from 100 meta-alignments sampled from nucleotide alignments which were ``reverse translated'' from the protein alignments and their corresponding coding sequences (\ref{fig:trees}B). Both trees have an identical topology, which is consistent with other published phylogenies~\cite{D12GC2007, DaLage2007}.

>>>>

\subsection{Inference of species trees}
Many phylogenetic methods require a species tree to inform the evolutionary relationships between sequences. In fact, the phylo-HMMs discussed previously used a species tree as an input, though we omitted this detail for clarity of exposition. Therefore, to support the curation step and other downstream analyses, we sought to infer phylogenetic trees from the aligned sequences. However, since the roots of phylogenetic trees are not identifiable with commonly used time-reversible substitution models, we repeated the orthology inference pipeline with the outgroup species \textit{Scaptodrosophila lebanonensis}. Afterwards, we inferred phylogenetic trees using the LG model of amino acid substitution from 100 meta-alignments sampled from alignments of single copy orthologous groups. We then combined them into a single consensus tree (Fig.~\ref{fig:trees}A). To provide a similar tree for the analysis of non-coding regions, we inferred phylogenetic trees using the GTR model of nucleotide substitution from 100 meta-alignments sampled from nucleotide alignments which were ``reverse translated'' from the protein alignments and their corresponding coding sequences (\ref{fig:trees}B).

Excluding the placement of \textit{D. obscura} (dobs), both trees have an identical topology, which is consistent with other published phylogenies. Additionally, three other nodes have short internal branches with bootstrap percentages below 100. These results indicate that not all sites and inference methods support the same topology, potentially as a result of incomplete lineage sorting. In such cases, gene trees can differ from the species tree, and we caution against using the species tree in gene-level analyses without further investigation if deviations from the true gene trees can significantly impact the results. However, as the internal branches are generally long and the bootstrap percentages for nearly all nodes are 100, the tree is generally highly resolved and therefore appropriate for use in population- or genome-level analyses without further incorporation of uncertainty.
